\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     HEADER
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{flushleft}
{\fontsize{24}{8}\selectfont \textbf{George Kalyvianakis}}\\
{\textcolor{subheading_gray}{\fontsize{16}{8}\selectfont \textbf{Software Engineer}}} \\
\vspace{6pt}
\href{mailto:george.kalyvianakis@gmail.com}{george.kalyvianakis@gmail.com} | \href{tel:+604903771}{+420 604 903 771} | Brno, Czech Republic \\
\vspace{3pt}
\href{https://github.com/CptGeo}{\bf Github} \textbullet{}
\href{https://www.linkedin.com/in/george-kalyvianakis/}{\bf LinkedIn} \\
\vspace{3pt}

\end{flushleft}

\hrule height 0.5pt
\vspace{3pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.63\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Siemens}
\descript{| Engineer Development }
\location{Feb 2023 – Sep 2024 | Brno, Czech republic}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Performed frontend development using \emph{TypeScript} and \emph{React} on top of the \emph{Siemens IX} component library. 
\item Developed a wide range of components, forms and pages.
\item Conducted thorough code reviews to ensure smooth integration to the codebase. 
\item Worked on the migration to NextJS and integration of TanStack Query for cache management. 
\item Maintained OpenAPI specification as part of the documentation process. \item Contributed to the backend by implementing an encryption mechanism to securely store sensitive files and also by setting up the basic unit testing environment.
\end{tightemize}
\sectionsep

\runsubsection{Honeywell}
\descript{| Software Engineer II }
\location{Nov 2021 – January 2023 | Brno, Czech republic}
\begin{tightemize}
\item Worked with \emph{PHP} with \emph{Nette Framework} and \emph{MySQL} on the backend.
\item Developed frontend using \emph{JavaScript} with \emph{jQuery}.
\item Designed and developed the \emph{Contract Editor} module, handling the entire process from database schema creation to the design of the MVC architecture and frontend design implementation.
\item Designed and optimized complex SQL queries to aggregate data from multiple tables, automating processes and reducing manual work for users.
\item Carried out bug fixes and maintenance, including code restructuring through pull requests, to improve system stability and code quality.
\end{tightemize}
\sectionsep

\runsubsection{Hotsoft}
\descript{| Junior Full-stack Developer }
\location{Aug 2018 – September 2021 | Rethymno, Greece}
\begin{tightemize}
\item Worked on website and e-commerce platform development using Contao CMS and CS-Cart, both using PHP and MySQL. 
\item Developed various webpage designs based on UI/UX prototypes provided in Adobe XD and Figma. 
\item Responsible for developing the \emph{ACS Courier} plugin for managing e-shop shipments and the \emph{XML Export} plugin to generate XML feeds from the store's product database.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Unity atlantic}
\descript{| React application for the exhibition of various dances and rhythms around the globe }
\location{June 2024 – Oct 2024 | Gerador.eu, Portugal }
\begin{tightemize}
\item Developed and deployed \textbf{\href{https://unityatlantic.org}{Unity Atlantic}}
\item Built using \emph{React} and \emph{JavaScript}.
\item Implemented headless \emph{Wordpress} setup for the backend.
\item Used \emph{Docker} for containerization and enchancement of CI/CD operations. 
\end{tightemize}
\runsubsection{Goodnet App}
\descript{| Android application for the Goodnet.gr news website, using React Native }
\location{Sep 2020 – Jun 2021 | Rethymno, Greece}
\sectionsep
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Hellenic Open University}
\descript{Msc. Information Systems}
\location{Exp. June 2025 | Patras, Greece}
\sectionsep

\subsection{Hellenic Mediterranean University}
\descript{Bsc. Electronics Engineering}
\location{Sept 2021 | Chania, Greece}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{PHP: 3+ years}
\location{JavaScript: 5+ years}
\location{Typescript: 2+ years}
\location{Java: 0+ years}
\location{Python: 0+ years}
\location{MySQL: 4+ years}
\location{HTML/CSS: 6+ years}
\sectionsep

\subsection{Technologies}
Git/Github \textbullet{} Docker \\
npm/pnpm \textbullet{} REST API \textbullet{} HTTP \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/CptGeo}{\bf CptGeo} \\
LinkedIn://  \href{https://www.linkedin.com/in/george-kalyvianakis/}{\bf George Kalyvianakis}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}